% ...existing code...
  % Create a table with two rows, one smaller than the other
  \noindent
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l}
    \textbf{\Large \href{https://www.linkedin.com/in/marthox/}{Mateo Gregory}} & \href{mailto:magremenez@gmail.com}{Email: magremenez@gmail.com}\\
    Systems Engineer \& Computer Science & \href{https://www.linkedin.com/in/marthox/}{LinkedIn: Marthox} \\
    Full-Stack Engineer & \href{https://www.marthox.com}{Website: Marthox.com} \\
    Project Manager & Phone: (+57) 316 4193085
  \end{tabular*}

  \vspace*{0.25cm}

  \noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
  Systems Engineer from Universidad del Valle, proficient in English (B2 certified), with knowledge and experience mainly in Python and JavaScript and some experience in Java, C\#, Ruby, and Elixir. I have experience in frameworks and libraries such as React, NodeJS, Django, Flask, Fast-Api, Phoenix, Svelte, and Rails. Version control (Git) and remote version control hosting platforms (GitHub).\\
  \noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

  \subsection*{Experience}

  \vspace*{0.2cm}
  \textbf{Software Engineer at \href{https://www.softserveinc.com/en-us}{SoftServe}} (February 2024 - Present)
  \hfill
  \vspace*{0.2cm}
  \begin{minipage}{\linewidth}
    \begin{itemize}[noitemsep]
      \item Contribute to the deployment and maintenance of integrations made for clients in the fields of biology and medicine, developing new features, fixing existing bugs, and refactoring legacy code.
      \item Manage serverless integrations, developing and deploying new features, fixing existing bugs, and refactoring the codebase, using AWS services such as Lambda, API Gateway, S3, DynamoDB, and SQS.
      \item Identify, prioritize, and resolve issues in integrations, monitoring application logs using tools like CloudWatch, Datadog, Sumologic, and Sentry, achieving 98\% uptime in integrations.
      \item Find and eliminate unused cloud resources, reducing infrastructure costs and improving application performance.
      \item Write performance tests for the application, identifying bottlenecks and improving application performance, achieving up to 800\% performance improvement in certain endpoints.
      \item Contribute to talks and workshops on software development, cloud services, and best practices in the company, achieving a better understanding of the technologies used in the company and by our clients.
      \item Contribute to social projects in the company, teaching and guiding students in software project development, achieving a better understanding of the technologies used in the industry and better preparation for the future of the students.
      \item Lead the Python community in the company, organizing talks, workshops, and hackathons, achieving a better understanding of the language and best practices in the company.
    \end{itemize}
    \hfill
  \end{minipage}
  Skills and tools: Python, TypeScript, JavaScript, AWS, Serverless, Lambda, API Gateway, S3, DynamoDB, SQS, CloudWatch, Datadog, Sumologic, Sentry, Git, Agile Development, Project Management, Performance Testing.

  \vspace{0.2cm}
  \textbf{Founder of the Community \href{https://www.parcha.tech/}{ParchaTech}} (August 2024 - Present)
  \hfill
  \vspace{0.2cm}
  \begin{minipage}{\linewidth}
    \begin{itemize}[noitemsep]
      \item Organize talks, workshops, and hackathons on software development, cloud services, and best practices, achieving a better understanding of the technologies used in the industry and better preparation for the future of the attendees.
      \item Create and maintain a community of software developers and technology enthusiasts, fostering collaboration, learning, and professional growth, achieving a better understanding of the technologies used in the industry and better preparation for the future of the members.
      \item Collaborate with companies and universities to organize talks, workshops, and hackathons, achieving a better understanding of the technologies used in the industry and better preparation for the future of the attendees.
      \item Collaborate with other software development communities to organize talks, workshops, and hackathons, fostering collaboration, learning, and professional growth, achieving a better understanding of the technologies used in the industry and better preparation for the future of the members.
    \end{itemize}
    \hfill
  \end{minipage}
  Skills and tools: Event Organization, Effective Communication, Collaboration, Leadership, Community Management, Software Development, Cloud Services, Best Practices, Information Technologies.
  \newpage

  \vspace*{0.2cm}
  \textbf{Full-Stack Engineer at \href{https://www.inchcape.com/}{Inchcape}} (October 2023 - February 2024)
  \hfill
  \vspace*{0.2cm}
  \begin{minipage}{\linewidth}
    \begin{itemize}[noitemsep]
      \item Contribute to more than ten websites in over five countries, maintaining, developing new features, fixing existing bugs, and refactoring the codebase, opening new markets expected to increase the company's revenue.
      \item Improve the user experience of the websites by developing country-specific features and following user-centered design principles, increasing user engagement and conversion rate.
    \end{itemize}
    \hfill
  \end{minipage}
  Skills and tools: C\# (C-Sharp), JavaScript, Html, Css, .Net, Umbraco, Atlassian, Jira, Git, Agile Software Development, Project Management.

  \vspace*{0.2cm}
  \textbf{Thesis Advisor at \href{https://www.univalle.edu.co/}{Universidad del Valle}} (June 2023 - December 2023)
  \hfill
  \vspace*{0.2cm}
  \begin{minipage}{\linewidth}
    \begin{itemize}[noitemsep]
      \item Guide students in the planning, development, and presentation of their theses, ensuring the quality and relevance of the projects.
      \item Provide constructive feedback and technical support in areas such as software development, artificial intelligence, and image processing, among others.
      \item Evaluate students' progress and provide guidance to improve their technical and research skills.
      \item Foster a collaborative and motivating learning environment, helping students achieve their academic and professional goals.
    \end{itemize}
    \hfill
  \end{minipage}
  Skills and tools: Mentoring, Software Development, Artificial Intelligence, Image Processing, Academic Research, Project Evaluation, Effective Communication.

  \vspace*{0.2cm}
  \textbf{Backend Engineer at \href{https://reserve.org/}{Reserve}} (July 2022 - May 2023)
  \hfill
  \vspace*{0.2cm}
  \begin{minipage}{\linewidth}
    \begin{itemize}[noitemsep]
      \item Optimize, refactor, and create more than ten API endpoints, implementing new features and fixing existing bugs, improving application stability to 99.98\%.
      \item Open the door to the Mexican market by integrating a third-party remittance provider, allowing users to withdraw and deposit cash, reaching a \$58.5 billion market.
      \item Improve the robustness of the application under different workload scenarios by implementing a customizable load testing tool, allowing the team to identify bottlenecks and improve application performance.
    \end{itemize}
    \hfill
  \end{minipage}
  Skills and tools: Python, JavaScript, Html, Css, FastAPI, React, Full-Stack Backend Development, RESTful API Development, API Integrations, Git, Agile Software Development, Project Management.

  \vspace*{0.2cm}
  \textbf{Full-Stack Engineer at \href{https://kommit.co/}{Kommit}} (October 2021 - July 2022)
  \hfill
  \vspace*{0.2cm}
  \begin{minipage}{\linewidth}
    \begin{itemize}[noitemsep]
      \item Improve the stability and functionality of \href{https://www.podnation.co/}{Podnation} by implementing new features and fixing existing bugs, maintaining the already high application uptime of 99.99\%.
      \item Launch a new feature for \href{https://www.podnation.co/}{Podnation} that allows users to create and share clips of their favorite podcasts, increasing user engagement and conversion rate by 10\%.
      \item Refactor and improve the hardware device controller for a US Military Foundation, significantly helping Parkinson's patients with speech difficulties, achieving a 99.99\% improvement in application robustness and stability.
    \end{itemize}
    \hfill
  \end{minipage}
  Skills and tools: JavaScript, Elixir, Ruby, React, AdonisJs, ElectronJs, Phoenix, Ruby on Rails, Full-Stack Development, Git, Agile Software Development, Project Management.

  \vspace*{0.2cm}
  \textbf{Full-Stack Freelance Engineer} (January 2021 - August 2021)
  \hfill
  \vspace*{0.2cm}
  \begin{minipage}{\linewidth}
    \begin{itemize}[noitemsep]
      \item Develop a specific interface for patients, demographically optimized for the target audience, implementing a custom React component library, increasing user engagement by 15\%.
      \item Create intuitive user interfaces, optimized for the target demographic to improve user experience and engagement, implementing a custom React component, increasing user engagement by 15\%.
      \item Build a role-based database model for efficient management of patient, doctor, and appointment data, ensuring data integrity and security.
      \item Oversee the deployment, configuration, and setup of the application on Digital Ocean servers using Docker, ensuring a smooth and efficient deployment process.
    \end{itemize}
    \hfill
  \end{minipage}
  Skills: JavaScript, Python, SQL, React, Flask, PostgreSQL, Docker, Digital Ocean, Freelance Development, Full-Stack Development, Project Management, Git, Agile Software Development, RESTful API Development.

  \vspace*{0.2cm}
  \textbf{Soft Skills}\\
  Autonomy, Teamwork, Goal Orientation, Leadership, Conflict Management, Teaching Skills, Active Listening, Clear Communication, Problem Solving, Flexibility, Creative Thinking, Time Management, Attention to Detail, User-Centered Approach, Analytical Skills, Emotional Intelligence, Project Management, Persistence.
  
  \subsection*{Education}
  \vspace*{0.2cm}
  \textbf{Bachelor's Degree in Systems Engineering at \href{https://www.univalle.edu.co/}{Universidad del Valle}} \hfill (June 2016 - December 2021)

  \noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

  \subsection*{Academic Experience}
  \vspace*{0.2cm}

  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l}
    \begin{minipage}{8.5cm}
      \textbf{Complexity and Optimization}
      \begin{itemize}[noitemsep, topsep=0pt]
        \item \href{https://github.com/MarthoxGJ/SATReductor}{SAT Reducer}
        \item \href{https://github.com/MarthoxGJ/ElectricStation}{Electric Station}
      \end{itemize}
      \hfill
    \end{minipage} & 
    \begin{minipage}{8.5cm}
      \textbf{Artificial Intelligence}
      \begin{itemize}[noitemsep, topsep=0pt]
        \item \href{https://github.com/MarthoxGJ/HexAgent}{Hex Agent}
        \item \href{https://github.com/MarthoxGJ/SokobanAgents}{Sokoban Agents}
      \end{itemize}
      \hfill
    \end{minipage}
    \vspace{0.4cm}\\
    \begin{minipage}{8.5cm}
      \textbf{Image Processing}
      \begin{itemize}[noitemsep, topsep=0pt]
        \item \href{https://github.com/MarthoxGJ/ImageProcessing}{Image Processing}
        \item \href{https://github.com/MarthoxGJ/MIA}{MIA}
      \end{itemize}
      \hfill
    \end{minipage} & 
    \begin{minipage}{8.5cm}
      \textbf{Networks}
      \begin{itemize}[noitemsep, topsep=0pt]
        \item \href{https://github.com/MarthoxGJ/GNS3Topology}{GNS3 Topology}
      \end{itemize}
      \hfill
    \end{minipage}
    \vspace{0.4cm}\\
    \begin{minipage}{8.5cm}
      \textbf{Software Development}
      \begin{itemize}[noitemsep, topsep=0pt]
        \item \href{https://github.com/MarthoxGJ/UVEnergy}{UV Energy}
        \item \href{https://github.com/MarthoxGJ/Nova}{Nova}
      \end{itemize}
      \hfill
    \end{minipage} & 
    \begin{minipage}{8.5cm}
      \textbf{Virtualization}
      \begin{itemize}[noitemsep, topsep=0pt]
        \item \href{https://github.com/MarthoxGJ/VBoxRESTAPI}{Virtual Box Rest API}
      \end{itemize}
      \hfill
    \end{minipage} \\
  \end{tabular*}

  \vspace*{0.2cm}
  \noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

  \subsection*{Extras}
  \vspace*{0.2cm}
  \begin{itemize}[noitemsep, topsep=0pt]
    \item Academic support monitor at Universidad del Valle
    \item Personalized support monitor at Universidad del Valle
    \item Attendee at the gamification workshop “Pioneras-Dev” by Edwin Gamboa
    \item Worked on drafting an academic article with Valeria Rivera, Emily Carvajal, and Jose Bernal
    \item Attendee at the 13th Colombian Computing Congress
  \end{itemize}

  \vspace*{0.2cm}
  \noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
