\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l}
\textbf{\Large \href{https://www.linkedin.com/in/stefhania-noguera/}{Stefhania Noguera Romero}} & \href{mailto:stefhanianogueraromero@gmail.com}{Email: stefhanianogueraromero@gmail.com}\\
Systems Engineer \& Computer Science & \href{https://www.linkedin.com/in/stefhania-noguera/}{LinkedIn: Stefhania Noguera} \\
Full-Stack Engineer & Phone: (+57) 322 6352232
\end{tabular*}

\vspace*{0.25cm}

\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
Systems Engineering student at Universidad del Valle with a solid grasp of JavaScript, HTML, and CSS. I am eager to gain practical experience and have a proven track record of quickly learning new technologies. My skills extend to UX, design, and other user experience-related skills, including proficiency with design tools such as Figma, also can work with collaborative tools like Atlassian, Jira, and Git. I am proficient in English (B2). I have experience working directly with clients, conducting requirement surveys, and participating in agile methodologies such as Scrum, including daily stand-ups, retrospectives, and other agile ceremonies. I am looking for an opportunity to apply my skills and knowledge in a challenging and dynamic environment, focusing on client-driven development to enhance user experiences.\\
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\subsection*{Experience}

\vspace*{0.2cm}
\textbf{Freelance Website Designer and Developer at \href{}{IntelDocs}} (November 2024 - Present)
\hfill
\vspace*{0.2cm}
\begin{minipage}{\linewidth}
\begin{itemize}[noitemsep]
    \item Design the IntelDocs website, a document management platform, using Figma, ensuring a user-friendly and intuitive interface.
    \item Design the content model and structure of the website, ensuring that the information is organized and presented in a clear and logical way for future modifications.
    \item Develop the IntelDocs website, using Astro, ensuring a responsive and user friendly design.
    \item Implement reactive components and animations using embeded React components, improving the user experience and engagement.
    \item Collaborate with the development team to ensure the design is implemented correctly and meets the requirements and expectations of the client.
    \item Conduct requirement surveys to gather and analyze client needs, ensuring the final product aligns with their expectations.
    \item Participate in agile ceremonies, such as daily stand-ups and retrospectives, to ensure continuous improvement and alignment within the team.
    \item Create the page using the server-side rendering framework Astro, ensuring fast loading times a smooth user experience and SEO optimization.
    \item Integrate the website with the CMS \href{https://www.contentful.com/}{contentful}, allowing the client to easily update and manage the content of the website without the need for technical knowledge.
    \item Create render safe components to ensure the website structure is not compromised by the client's changes, ensuring the website's integrity and consistency.
    \item Focus on client-driven development to enhance user experiences by optimizing design and functionality based on client feedback.
\end{itemize}
\hfill
\end{minipage}
Skills and tools: Figma, HTML, CSS, JavaScript, Astro, React, Contentful, Design, User Experience, User Interface, Responsive Design, SEO Optimization, Collaboration, Communication, Problem Solving, Creativity, Time Management, Attention to Detail, Client Management.

\vspace*{0.2cm}
\textbf{Software Engineer at Aux at \href{https://www.univalle.edu.co/}{Universidad del Valle}} (August 2022 - Present)
\hfill
\vspace*{0.2cm}
\begin{minipage}{\linewidth}
\begin{itemize}[noitemsep]
    \item Developed and maintained automatic monthly reports using Google Sheets and Google Apps Script, reducing the time spent on manual reporting by at least 80\%.
    \item Created custom templates for the reports, allowing for easy customization and adaptation to different departments and needs.
    \item Improved the accuracy and reliability of the reports by implementing data validation and error handling, ensuring the quality of the data and the reports.
    \item Lead the project from conception to implementation, coordinating with stakeholders, gathering requirements, and delivering the final product on time and within budget.
    \item Engage directly with clients to understand their needs and provide regular updates on project progress.
    \item Optimize data processing and server-side logic to enhance client experiences and ensure smooth execution of the product.
\end{itemize}
\hfill
\end{minipage}
Skills and tools: Google Sheets, Google Apps Script, Automation, Data Analysis, Data Visualization, Project Management, Communication, Problem Solving, Requirements Gathering, User-Centered Design.

\newpage

\vspace*{0.2cm}
\textbf{Freelance Web Developer at \href{}{SIGEIN S.A.S}} (June 2023 - October 2023)
\hfill
\vspace*{0.2cm}
\begin{minipage}{\linewidth}
\begin{itemize}[noitemsep]
    \item Developed user interfaces tailored to client requirements, ensuring a user-friendly and intuitive experience.
    \item Collaborated with a team focused on rigorous testing to minimize errors and ensure a high-quality product.
    \item Followed agile methodologies to deliver projects on time and within budget, ensuring client satisfaction.
    \item Participate and collaborate in agile ceremonies, such as sprint planning, daily stand-ups, and retrospectives, ensuring alignment and communication within the team.
    \item Conduct requirement surveys to gather client needs and ensure the final product meets their expectations.
    \item Focus on client-driven development to deliver user interfaces tailored to client requirements, ensuring a user-friendly and intuitive experience.
\end{itemize}
\hfill
\end{minipage}
Skills and tools: HTML, CSS, JavaScript, Agile Software Development, User Interface Design, User Experience, Collaboration, Communication, Problem Solving, Creativity, Time Management, Attention to Detail, Client Management, Requirement Survey, Scrum, Agile Ceremonies, Client-Driven Development.
\vspace{1cm}

\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\vspace*{0.2cm}
\textbf{Soft Skills}\\
Autonomy, Teamwork, Communication, Problem Solving, Creativity, Time Management, Attention to Detail, Client Management, Leadership, Adaptability, Emotional Intelligence, Critical Thinking, Decision Making, Conflict Resolution, Negotiation, Stress Management, Empathy, Active Listening, Persuasion\\

\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\subsection*{Education}
\vspace*{0.2cm}
\textbf{Bachelor's Degree in Systems Engineering at \href{https://www.univalle.edu.co/}{Universidad del Valle}} \hfill

\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\subsection*{Academic Experience}
\vspace*{0.2cm}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l}
\begin{minipage}{8.5cm}
    \textbf{Artificial Intelligence}
    \begin{itemize}[noitemsep, topsep=0pt]
    \item \href{https://github.com/Yi0nn/Informe-IA}{Breast Cancer Prediction}
    \item \href{https://github.com/Yi0nn/Proyecto-IA}{Labyrinth Solver}
    \end{itemize}
    \hfill
\end{minipage}&
\begin{minipage}{8.5cm}
    \textbf{Complexity and Optimization}
    \begin{itemize}[noitemsep, topsep=0pt]
    \item \href{https://github.com/Yi0nn/ProyectoADA2}{Thermal Units Optimization}
    \item \href{https://github.com/MarthoxGJ/ElectricStation}{Electric Station}
    \end{itemize}
    \hfill
\end{minipage}
\vspace{0.4cm}\\
\begin{minipage}{8.5cm}
    \textbf{DevOps}
    \begin{itemize}[noitemsep, topsep=0pt]
    \item \href{https://github.com/Yi0nn/tallergithubactions}{GitHub Actions Workshop}
    \end{itemize}
    \hfill
\end{minipage} & 
\begin{minipage}{8.5cm}
    \textbf{API Development}
    \begin{itemize}[noitemsep, topsep=0pt]
    \item \href{https://github.com/Yi0nn/ejemploapi}{Students API}
    \end{itemize}
    \hfill
\end{minipage}
\vspace{0.4cm}\\
\begin{minipage}{8.5cm}
    \textbf{Software Development}
    \begin{itemize}[noitemsep, topsep=0pt]
    \item \href{https://github.com/JoseBecerra02/Sweet-Pet-Shop}{Sweet Pet Shop}
    \item \href{https://github.com/RoseRossi/Visual_Novel}{Visual Novel} \href{https://www.figma.com/design/oyYTHggT5Qzmg5J0RZZVwx/Visual_Novel?m=auto&t=cjb55xFfPUILOhhu-1}{(Figma)}
    \end{itemize}
    \hfill
\end{minipage} & 
\begin{minipage}{8.5cm}
    \textbf{UX Design}
    \begin{itemize}[noitemsep, topsep=0pt]
    \item \href{https://github.com/CriistiianDM/Red-wheels}{Red Wheels} \href{https://www.figma.com/design/yonGMfbUZSB5YkmaDHPkU5/Desarrollo?m=auto&t=cjb55xFfPUILOhhu-1}{(Figma)}
    \item \href{https://www.figma.com/design/KMyxhoEvgbkZM3mlT51GvK/EcoBuddy?m=auto&t=cjb55xFfPUILOhhu-1}{Eco Buddy}
    \end{itemize}
    \hfill
\end{minipage} \\
\end{tabular*}

\vspace*{0.5cm}
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
